Constant Error Tolerance Computational Fuzzy Extractors

### 2014-02-06 constantRate/ConstCompFuzzExt.tex
Moved second cons proofs to appendix

We give a brief outline of the proof here, the full proof is in \apref{app:security of main cons}.
It is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))\le \ngl(n)$.  Let $\mathcal{I}$ be the set of indices that exists in \defref{def:block guessable}, the distribution $C'$ is defined as a uniform codeword conditioned on the values of $C$ and $C'$ being equal on all indices outside of $\mathcal{I}$.  We first note that $C'$ has sufficient entropy.  That is, $\Hav(C' |P) =\Hav(C' | C_{\mathcal{I}^c} = C'_{\mathcal{I}^c}) = |C| - |\mathcal{I}^c|$.  It is left to show $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P)) \le \ngl(n)$.
%Define the distribution $X$ as follows:
%\[X_i =
%\begin{cases}
%W_i & C_i = 0\\
%R_i & C_i = 1.
%\end{cases}\]
The outline for the rest of the proof is as follows:
\begin{itemize}
\item Let $D$ be a distinguisher between $(C, P)$ and $(C', P)$, since $P$ is a collection of obfuscated programs there exists a simulator, $S$~(outputting a single bit), such that $\Pr[D(C, P)=1]$ is close to $\Pr[S^{\mathcal{O}}(C)=1]$.
\item Show that even an unbounded $S$ making a polynomial number of queries to the stored points cannot distinguish between $C$ and $C'$.  That is, $\delta(S^{\mathcal{O}}(C),S^{\mathcal{O}}(C'))$ is small.
\item By the security of obfuscation, $\Pr[S^{\mathcal{O}}(C')=1]$ is close to $\Pr[D(C', P)=1]$.
\end{itemize}

@@

\subsection{Correctness of \consref{cons:first construction}}
\label{sec:correct first cons}
We begin by showing that the probability of a single $1\rightarrow 0$ bit flip in $c$ is negligible.
%Most of the effort in showing the correctness of \consref{cons:first construction} is showing that $\dis(w, w')\leq t$ implies $\dis(c, c')\leq t$.  However, we start by justifying our use of unidirectional codes.
\begin{lemma}
\label{lem:no 1 to 0 flips}
The probability of at least one $1\rightarrow 0$ bit flip~(an obfuscation of a random block being interpreted as the obfuscation of the point) is $ \ell/2^n = \ngl(n)$.
\end{lemma}
\begin{proof}
Recall that $c$ contains at most $\ell$ $1$s.  Since $w'$ is chosen independently of the points $r_i$, this probability is the size of each block, that is $\Pr[r_i =w_i']  = 1/2^n$. Since the $r_i$ are chosen independently, one has,
\begin{align*}
\Pr[\text{no $1\rightarrow 0$ flips}] &\geq 1-\Pr[\text{some }r_i = w_i']\\
&\geq 1-\ell \frac{1}{2^n} = 1-\frac{\poly(n)}{2^n} = \ngl(n)
\end{align*}
\end{proof}

@@

\subsection{Discussion}
\label{sec:discussion}
Security of \consref{cons:first construction} relies on a large number of dimensions which are unpredictable.  Correction occurs for a small number of dimensions that are allowed to vary completely.  As described in \secref{sec:sec of construction}, \consref{cons:first construction} is not secure for an arbitrary min-entropy source, it must contain a significant number of dimensions that are hard to guess by equality queries~(meaning they have min-entropy).

@@

We consider what entropy is necessary for security.  The simplest type of unguessable block distribution is where each block is independent and has super-logarithmic entropy~(\clref{cl:independent high ent}).  For this type of source the required entropy is $\Hoo(W) = \ell\omega(\log n)$.  This yields:
\[
\Huse = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \Theta(t n) + \log {\ell \choose t}\right).
\]
When $t =\Theta(\ell)$, then $\Huse<0$ and the output entropy is $|C| -\beta$~(if $C$ is a constant rate, this is $\Theta(\ell)$).
Thus, \consref{cons:first construction} achieves for security for unguessable block distributions with negative $\Huse$ when $t = \Theta(\ell)$.  %We achieve security when $\Huse<0$, constant error tolerance, and extract a constant fraction of $n$ when $t = \Theta(\ell)$ and $\ell = O(n)$.
%When $ \ell , t, n$ to be the same order provides a natural balance of parameters.

@@

\section{Sample-then-Obfuscate}
\label{sec:sampling}
\consref{cons:first construction} is a computational fuzzy extractor with $\Huse<0$.  In this section, we present a generalization where blocks are not individually obfuscated, instead several blocks are obfuscated together~(these blocks are selected using an oblivious sampler).  The main advantage of this approach is reduces the required entropy in each block of the source.  Unfortunately, obfuscating multiple blocks together decreases the effective error tolerance.  Thus, we have a tradeoff between individually required entropy and supported error tolerance.  In ordering for sampling to work properly, we need a source where most blocks are likely to contribute some entropy.

@@

\defref{def:unordered source} is a generalization of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}) where blocks must have entropy conditioned on the value of previous blocks.  An unordered block source is also a strengthening of an unguessable block distribution~(\defref{def:block guessable}).  An unordered block source requires there to be worst case entropy while an unguessable block distribution only requires average conditional entropy.  However, we achieve security for significantly lower entropy levels than were needed for unguessable block distributions.

@@

The main change in \consref{cons:sampling} is that the obfuscated values are concatenated blocks symbols of $W$.  This paradigm is similar to \emph{sample-then-extract} from the locally computable extractors literature~\cite{lu2002hyper,vadhan2003constructing}.  For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.  A crucial difference is the use of a computational primitive~(obfuscation) allows us to sample multiple times and only argue that each $v_i$ has sufficient has individual entropy.  In the information-theoretic setting, it would be necessary to argue about the joint entropy of the obfuscated values.  Our construction uses a na\"{i}ve sampler that takes truly random samples, but the public randomness may be substantially decreased by using more sophisticated samplers.  Goldreich provides an introduction to samplers~\cite{goldreich1997sample}.

@@

\subsection{Security of \consref{cons:sampling}}
In order to show security \consref{cons:sampling}, we show that with overwhelming probability each of the selected $V_i$ has super-logarithmic entropy on its own~(samplers will select ``enough'' of the good blocks of $W$ each time).  We can then argue that $V_1,..., V_\ell$ forms a block-unguessable distribution.  Then \consref{cons:sampling} is just the first construction applied to $V_1,.., V_\ell$ and security follows by \thref{thm:security of cons}.  We begin by showing that each $V_i$ is statistically close to a high entropy distribution.

%\bnote{think about how to make this work when $\eta = \Theta(1)$.  Will make probabilities gross.  Probably not for submission.}
\begin{lemma}
\label{lem:sampling works}
Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta\le \gamma(1- \Theta(1)))$-unordered block source and let $\eta = \omega(\log n) \le  o(\gamma)$.  Consider some fixed $i$, there exists $\epsilon_{sam} = O(e^{-\eta}) = \ngl(n)$ and $\alpha' = \alpha\eta(\gamma-\beta-\eta)/\gamma = \omega(\log n)$ such that 
\[
\Pr[\Hoo(V_i | \Lambda) \geq \alpha'] \geq 1- \epsilon_{sam}.
\]
\end{lemma}
\begin{proof}
Consider some fixed $i$.  Let $\Lambda$ represent the random variable of all the coins used by $\sample$ and $\lambda$ be some particular outcome.
For each particular value of $w_1,..., w_\gamma$ there exists some set $\mathcal{I}$ of size $\gamma - \beta = \Theta(\gamma)$ such that each block $j\in \mathcal{I}, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}, W_{j+1}=w_{j+1},..., W_\gamma = w_\gamma) \geq \alpha$.  Since this is a worst case guarantee for all $\lambda$, 
\[
\Hoo(V_i |\lambda ) \geq \alpha \times |\{\text{indices in }\mathcal{I}\text{ sampled in }V_i\}|.
\]

%
%\begin{lemma}
%
%Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma(1/2-\Theta(1)))$-unordered block source.  Let $\eta = \Omega(\log n)$. Consider some fixed $i$, the distribution $V_{i}, \Lambda_i$ is $(\ngl(n)+ 2^{-\Omega(n)})$-close to a distribution $V', U_{r_{sam}}$ where for all $u\in U_{r_{sam}}$ $V' | U_{r_{sam}}=u$, $\Hoo(V' | U_{r_{sam}}=u) \geq \Omega(\alpha\times (1-2\times \beta) \times \eta) = \omega(\log n) = \alpha'$.
%\end{lemma}
%\begin{proof}
%By~\cite[Lemma 9]{vadhan2003constructing}, noting that the na\"{i}ve sampler is optimum in necessary samples and we use $\eta = \omega(\log n)$ samples.  \bnote{need someone to check parameters, in the abstract, I am fairly sure the statement makes sense, but I could easily have messed something up}\bnote{even if this is right it needs to be expanded.  too much for a reader to digest.}
%\end{proof}

\noindent
We can then argue that all $V_i$ simultaneously have individual entropy with good probability:
\begin{corollary}
\label{cor:samp sec}
Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma(1-\Theta(1)))$-unordered block source.  Let $\eta = \omega(\log n) = o(\gamma)$ and let $\epsilon_{sam}, \alpha'$ be as in \lemref{lem:sampling works}.  Then $\Pr[\exists i, \Hoo(V_i | \Lambda) \not \ge \alpha'] \leq 1-\ell\epsilon_{sam}$.
%[V_i(V, \Lambda)$ is $(\ell\epsilon_{sam})$-close to a distribution $(V', U_{\ell\times r_{sam}})$ where for $u\in U_{\ell\times r_{sam}}$ for all $i$, $\Hoo(V_i' | U_{\ell\times r_{sam}} =u)\geq \alpha'$.
\end{corollary}
\begin{proof}
Union bound over the probability in \lemref{lem:sampling works}.
%Hybrid argument over the statistical distance in \lemref{lem:sampling works}.
\end{proof}

@@

\subsection{Correctness of \consref{cons:sampling}}
\label{sec:correct sampling}
The argument that $1\rightarrow 0$ flips are unlikely carries over from \consref{cons:first construction}.  This probability is at most $\ell/\mathcal{Z}^\eta$.  We now show that there are few enough $0\rightarrow 1$ flips with overwhelming probability.  Let $t'$ be the capacity of $C$.  We show that $\Pr_{(v, v')\leftarrow (V, V')}[\dis(v, v')\ge t'] <\ngl(n)$.

\begin{lemma}
Let $n, W$ be as above and Let $C$ be a code that corrects $t'$ $0\rightarrow 1$ bit errors where $t' =\Theta(\ell)$.  Let $\mu = -\log(1-t'/(2\ell))/2 = \Theta(1)$, if $t \leq \mu(\gamma - \eta)/\eta$, then $\Pr[\dis(v, v')\leq t']\geq 1-O(2^{-\ell})$ where the probability is over the coins of $\gen$.  %That is, for any $t\leq \mu(\gamma-\eta)/\eta$, \consref{cons:sampling} is correct with overwhelming probability.
\end{lemma}

@@

>>>>

We give a brief outline of the proof here, the proof is in \apref{app:security of main cons}.
It is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))\le \ngl(n)$.  Let $\mathcal{I}$ be the set of indices that exists in \defref{def:block guessable}, the distribution $C'$ is defined as a uniform codeword conditioned on the values of $C$ and $C'$ being equal on all indices outside of $\mathcal{I}$.  We first note that $C'$ has sufficient entropy.  That is, $\Hav(C' |P) =\Hav(C' | C_{\mathcal{I}^c} = C'_{\mathcal{I}^c}) = |C| - |\mathcal{I}^c|$.  It is left to show $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P)) \le \ngl(n)$.
%Define the distribution $X$ as follows:
%\[X_i =
%\begin{cases}
%W_i & C_i = 0\\
%R_i & C_i = 1.
%\end{cases}\]
The outline for the rest of the proof is as follows:
\begin{itemize}
\item Let $D$ be a distinguisher between $(C, P)$ and $(C', P)$, since $P$ is a collection of obfuscated programs there exists a simulator, $S$~(outputting a single bit), such that $\Pr[D(C, P)=1]$ is close to $\Pr[S^{\mathcal{O}}(C)=1]$.
\item Show that even an unbounded $S$ making a polynomial number of queries to the stored points cannot distinguish between $C$ and $C'$.  That is, $\delta(S^{\mathcal{O}}(C),S^{\mathcal{O}}(C'))$ is small.
\item By the security of obfuscation, $\Pr[S^{\mathcal{O}}(C')=1]$ is close to $\Pr[D(C', P)=1]$.
\end{itemize}

@@

\subsection{Correctness of \consref{cons:first construction}}
\label{sec:correct first cons}
We begin by showing that the probability of a single $1\rightarrow 0$ bit flip in $c$ is negligible.
%Most of the effort in showing the correctness of \consref{cons:first construction} is showing that $\dis(w, w')\leq t$ implies $\dis(c, c')\leq t$.  However, we start by justifying our use of unidirectional codes.
\begin{lemma}
\label{lem:no 1 to 0 flips}
The probability of at least one $1\rightarrow 0$ bit flip~(an obfuscation of a random block being interpreted as the obfuscation of the point) is $ \ell/2^n = \ngl(n)$.
\end{lemma}
\begin{proof}
Recall that $c$ contains at most $\ell$ $1$s.  Since $w'$ is chosen independently of the points $r_i$, this probability is the size of each block, that is $\Pr[r_i =w_i']  = 1/2^n$. Since the $r_i$ are chosen independently, one has,
\[
\Pr[\text{no $1\rightarrow 0$ flips}] \geq 1-\Pr[\text{some }r_i = w_i']\geq 1-\sum_{i=1}^\ell \Pr[r_i = w_i'] \geq 1-\ell \frac{1}{2^n}.
\]
\end{proof}

@@

\subsection{Discussion}
\label{sec:discussion}
Security of \consref{cons:first construction} relies on a large number of dimensions which are unpredictable.  Correction occurs for a small number of dimensions that are allowed to vary completely.  As described in \secref{sec:sec of construction}, \consref{cons:first construction} is not secure for an arbitrary min-entropy source, it must contain a significant number of dimensions that are hard to guess by equality queries.

@@

We consider what entropy is necessary for security.  The simplest type of unguessable block distribution is where each block is independent and has super-logarithmic entropy~(\clref{cl:independent high ent}).  For this type of source the required entropy is $\Hoo(W) = \ell\omega(\log n)$.  This yields:
\[
\Huse = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \Theta(t n) + \log {\ell \choose t}\right).
\]
When $t =\Theta(\ell)$ and the entropy of each block is $o(n)$, then $\Huse<0$ and the output entropy is $|C| -\beta$~(if $C$ is a constant rate, this is $\Theta(\ell)$).
%Thus, \consref{cons:first construction} achieves for security for unguessable block distributions with negative $\Huse$ when $t = \Theta(\ell)$.  %We achieve security when $\Huse<0$, constant error tolerance, and extract a constant fraction of $n$ when $t = \Theta(\ell)$ and $\ell = O(n)$.
%When $ \ell , t, n$ to be the same order provides a natural balance of parameters.

@@

\section{Sample-then-Obfuscate}
\label{sec:sampling}
\consref{cons:first construction} is a computational fuzzy extractor with $\Huse<0$.  In this section, we present a generalization where blocks are not individually obfuscated, instead several blocks are obfuscated together~(these blocks are selected using an oblivious sampler).  The main advantage of this approach is reduces the required entropy in each block of the source.  Unfortunately, obfuscating multiple blocks together decreases the effective error tolerance.  Thus, we have a tradeoff between individually required entropy and supported error tolerance.  In ordering for sampling to work properly, we need a source where a constant fraction of blocks are likely to contribute some entropy.

@@

\defref{def:unordered source} is a generalization of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}) where blocks must have entropy conditioned on the value of previous blocks.  An unordered block source is also a strengthening of an unguessable block distribution~(\defref{def:block guessable}).  An unordered block source requires there to be worst case entropy while an unguessable block distribution only requires average conditional entropy.  However, we achieve security for significantly lower entropy levels than for unguessable block distributions.

@@

The main change in \consref{cons:sampling} is that the obfuscated values are concatenated blocks symbols of $W$.  This paradigm is similar to \emph{sample-then-extract} from the locally computable extractors literature~\cite{lu2002hyper,vadhan2003constructing}.  For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.  A crucial difference is the use of a computational primitive~(obfuscation) allows us to sample multiple times and only argue that each $v_i$ has individual entropy.  In the information-theoretic setting, it would be necessary to argue about the joint entropy of the obfuscated values.  Our construction uses a na\"{i}ve sampler that takes truly random samples, but the public randomness may be substantially decreased by using more sophisticated samplers.  Goldreich provides an introduction to samplers~\cite{goldreich1997sample}.

@@

\subsection{Security of \consref{cons:sampling}}
In order to show security \consref{cons:sampling}, we show that with overwhelming probability each of the selected $V_i$ has super-logarithmic entropy on its own~(samplers will select ``enough'' of the good blocks of $W$ each time).  We can then argue that $V_1,..., V_\ell$ forms a block-unguessable distribution.  Then \consref{cons:sampling} is just the first construction applied to $V_1,.., V_\ell$ and security follows by \thref{thm:security of cons}.  We begin by showing that each $V_i$ is statistically close to a high entropy distribution~(proof in \apref{sec:proof of sampling lemma}).

%\bnote{think about how to make this work when $\eta = \Theta(1)$.  Will make probabilities gross.  Probably not for submission.}
\begin{lemma}
\label{lem:sampling works}
Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta\le \gamma(1- \Theta(1)))$-unordered block source and let $\eta = \omega(\log n) \le  o(\gamma)$.  Consider some fixed $i$, there exists $\epsilon_{sam} = O(e^{-\eta}) = \ngl(n)$ and $\alpha' = \alpha\eta(\gamma-\beta-\eta)/\gamma = \omega(\log n)$ such that 
\[
\Pr_{\lambda\leftarrow \Lambda}[\Hoo(V_i | \Lambda= \lambda) \geq \alpha'] \geq 1- \epsilon_{sam}.
\]
\end{lemma}
%
%\begin{lemma}
%
%Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma(1/2-\Theta(1)))$-unordered block source.  Let $\eta = \Omega(\log n)$. Consider some fixed $i$, the distribution $V_{i}, \Lambda_i$ is $(\ngl(n)+ 2^{-\Omega(n)})$-close to a distribution $V', U_{r_{sam}}$ where for all $u\in U_{r_{sam}}$ $V' | U_{r_{sam}}=u$, $\Hoo(V' | U_{r_{sam}}=u) \geq \Omega(\alpha\times (1-2\times \beta) \times \eta) = \omega(\log n) = \alpha'$.
%\end{lemma}
%\begin{proof}
%By~\cite[Lemma 9]{vadhan2003constructing}, noting that the na\"{i}ve sampler is optimum in necessary samples and we use $\eta = \omega(\log n)$ samples.  \bnote{need someone to check parameters, in the abstract, I am fairly sure the statement makes sense, but I could easily have messed something up}\bnote{even if this is right it needs to be expanded.  too much for a reader to digest.}
%\end{proof}

\noindent
We can then argue that all $V_i$ simultaneously have individual entropy with good probability:
\begin{corollary}
\label{cor:samp sec}
Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma(1-\Theta(1)))$-unordered block source.  Let $\eta = \omega(\log n) = o(\gamma)$ and let $\epsilon_{sam}, \alpha'$ be as in \lemref{lem:sampling works}.  Then $\Pr_{\lambda\leftarrow \Lambda}[\exists i, \Hoo(V_i | \Lambda = \lambda) \not \ge \alpha'] \leq 1-\ell\epsilon_{sam}$.
%[V_i(V, \Lambda)$ is $(\ell\epsilon_{sam})$-close to a distribution $(V', U_{\ell\times r_{sam}})$ where for $u\in U_{\ell\times r_{sam}}$ for all $i$, $\Hoo(V_i' | U_{\ell\times r_{sam}} =u)\geq \alpha'$.
\end{corollary}
\begin{proof}
Union bound over the probability in \lemref{lem:sampling works}.
%Hybrid argument over the statistical distance in \lemref{lem:sampling works}.
\end{proof}

@@

\subsection{Correctness of \consref{cons:sampling}}
\label{sec:correct sampling}
The argument that $1\rightarrow 0$ flips are unlikely carries over from \consref{cons:first construction}.  This probability is at most $\ell/\mathcal{Z}^\eta$.  We now show that there are few enough $0\rightarrow 1$ flips with overwhelming probability.  Let $t'$ be the capacity of $C$.  We show $\Pr_{(v, v')\leftarrow (V, V')}[\dis(v, v')\ge t'] <\ngl(n)$.  The proof is in \apref{sec:sampling errors}.

\begin{lemma}
\label{lem:sampling errors}
Let $n, W$ be as above and Let $C$ be a code that corrects $t'$ $0\rightarrow 1$ bit errors where $t' =\Theta(\ell)$.  Let $\mu = -\log(1-t'/(2\ell))/2 = \Theta(1)$, if $t \leq \mu(\gamma - \eta)/\eta$, then $\Pr[\dis(v, v')\leq t']\geq 1-O(2^{-\ell})$ where the probability is over the coins of $\gen$.  %That is, for any $t\leq \mu(\gamma-\eta)/\eta$, \consref{cons:sampling} is correct with overwhelming probability.
\end{lemma}

@@

\section{Proof of \lemref{lem:sampling works}}
\label{sec:proof of sampling lemma}
\begin{proof}
Consider some fixed $i$.  Let $\Lambda$ represent the random variable of all the coins used by $\sample$ and $\lambda$ be some particular outcome.
For each particular value of $w_1,..., w_\gamma$ there exists some set $\mathcal{I}$ of size $\gamma - \beta = \Theta(\gamma)$ such that each block $j\in \mathcal{I}, \Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}, W_{j+1}=w_{j+1},..., W_\gamma = w_\gamma) \geq \alpha$.  Since this is a worst case guarantee for all $\lambda$, 
\[
\Hoo(V_i |\lambda ) \geq \alpha \times |\{\text{indices in }\mathcal{I}\text{ sampled in }V_i\}|.
\]

\section{Proof of \lemref{lem:sampling errors}}
\label{sec:sampling errors}
